### 2021-10-17 docs/manuscript/manuscript.tex
Improve S5 Fig. caption

\paragraph*{S5 Fig.}
\label{S5_Fig}
{\bf Dynamics of expression of topology number 9.}
The dynamics of expression is shown from $t = 5$ to $t = 150$. The red line
represents the expression level of the gene C along the morphogenetic field,
whereas the dotted line represents the expression level of gene A. The
striped pattern of gene expression can be seen for both genes since $t = 80$.

>>>>

\paragraph*{S5 Fig.}
\label{S5_Fig}
{\bf Dynamics of expression of topology number 9.}
The dynamics of expression is shown from $t = 5$ to $t = 150$, where this
topology reaches its steady state expression. The red line
represents the expression level of the gene C along the morphogenetic field,
whereas the dotted line represents the expression level of gene A. The
striped pattern of gene expression can be seen for both genes since $t = 80$.
